### 2021-05-14 LaTeX-ACM/sections/paper.tex
small tweaks

We have avoided augmenting \cm with centralized components and third-party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks. However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX). We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to improve performance, but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

% = = = = = = = = = = = = = = = = = = = = = = = = =  %
		% MM:  Dont know to merger the following paragraph with this section?

@@

 \subsubsection*{Availability} 
The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository\footnote{\CallMarketRepo}. We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]}.

>>>>

We have avoided augmenting \cm with centralized components and third party services as our research question concerns the feasibility of a system with a minimum of regulatory hooks. However from a regulatory stance, there is a big difference between an architecture where the centralized component is publicly visible and interacted with by users (\eg most DEXes, roll-up architectures like Loopring, and commit-chain solutions like TEX). We consider an alternative design that is almost as difficult to regulate as a fully on-chain solution. In this design, an off-chain component is introduced to boost performance but it only interacts with the Ethereum network and never directly with traders. Traders still only interact with Ethereum.

@@

 \subsubsection*{Availability} 
The Solidity source code for \cm, Truffle test files, and Arbitrum dependencies are available in a GitHub repository (non-anonymous link omitted). We have also deployed \cm on Ethereum's testnet Rinkeby with flattened (single file) source code of just the \cm base class and priority queue implementations. It is visible and can be interacted with here: \href{https://rinkeby.etherscan.io/address/0x0d91de29c531d074853a5cef7cf9dfeb9c6ec4e0}{[etherscan.io]}; while the Arbitrum variant is here: \href{https://explorer.arbitrum.io/#/tx/0x1828d7eb6a7a9b9ec479f07e8149c6172bb89a101571963b5cf690132bdf009b}{[explorer.offchainlabs.com]}.
